Towards Optimized Keyword Hash Maps for Clojure

### 2024-08-23 paper/paper.tex
regen paper
typo

\pdfoutput=1
\usepackage[backend=bibtex]{biblatex}

@@

\special{papersize=8.5in,11in}
\setlength{\pdfpageheight}{\paperheight}
\setlength{\pdfpagewidth}{\paperwidth}

@@

Our approach to speeding up the hash-map implementation
is related to \textit{storage strategies}
by Bolz et. al~\cite{Bolz13storagestrategies}.
They observe that dynamically typed languages often use
heterogenous collections as homogeneous, and present
optimizations to take advantage of this fact.

>>>>

%\pdfoutput=1
\usepackage[backend=bibtex]{biblatex}

@@

\special{papersize=8.5in,11in}
%\setlength{\pdfpageheight}{\paperheight}
%\setlength{\pdfpagewidth}{\paperwidth}

@@

Our approach to speeding up the hash-map implementation
is related to \textit{storage strategies}
by Bolz et. al~\cite{Bolz13storagestrategies}.
They observe that dynamically typed languages often use
heterogeneous collections as homogeneous, and present
optimizations to take advantage of this fact.
